HTW Model e1

### 2024-03-22 Model/htw_model_e1.qmd
add e2 and e3 modeling

ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
nbins <- 3
e1Sbjs <- ds |> group_by(id,condit) |> summarise(n=n())
fd <- readRDS(here("data/e1_08-21-23.rds"))
test <- testE1 <-  fd |> filter(expMode2 == "Test") 
testAvg <- testE1 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vxAvg=mean(vx),distAvg=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

@@

@@

pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvg,by=c("id","condit","bandInt")) 
pd <- post_dat |> rename("bandInt"=x) |> left_join(testAvg,by=c("id","condit","bandInt"))

@@

# extract id's from term column - Intercept is id 1, term=ModelEXAM doesn't have an id, so don't include
k <- b3_coef |> filter(term!="Intercept" & term!="ModelEXAM") |> mutate(id=as.factor(str_extract(term,"\\d+"))) |> left_join(testAvg |> filter(bandInt==100) |> ungroup() |> select(-bandType,-vb,-bandInt),by="id") |> 
  mutate(exam_coef=exam_coef)

@@

k2 <- k |> filter(parType=="Model") |> mutate(id=reorder(id,Estimate), Estimate=Estimate+exam_coef) |> 
  select(id,condit,Estimate) |> left_join(testAvg,by=c("id","condit"))

@@

group_pred <- post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=val,y=vbLab,col=Resp)) + 
  stat_pointinterval(position=position_dodge(.5), alpha=.9) + 
  scale_color_manual(values=wes_palette("AsteroidCity2"))+
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
  labs(title="Posterior Predictions - Testing Stage",y="Velocity Band (lower bound)", x="X Velocity") +
theme(legend.title=element_blank(),axis.text.y = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

```{r}
#| fig-height: 12
#| fig-width: 11
 post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=condit,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~Resp, axes = "all",ncol=3,scale="free")

post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free")

p1 <- post_dat_l |> 
  filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

p2 <- post_dat_l |> 
  filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=Resp,y=val,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

@@

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=condit)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~vbLab, axes = "all",ncol=2,scale="free")

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=Resp,y=val,fill=condit)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~vbLab, axes = "all",ncol=2,scale="free")

@@

# d <- testAvg |> left_join(full_comparison, by=c("id","condit")) |> filter(Fit_Method=="Test_Train")
# 
# 
# 
# d |> ggplot(aes(x=vb,y=vx,fill=condit)) + stat_bar + facet_wrap(Fit_Method~Best_Model2,ncol=2)
# 
# d |> 
#   group_by(condit,Fit_Method,Best_Model) |> 
#   mutate(nGrp2=n()) |>
#   filter(abs(Error_difference)>15) |> 
#   ggplot(aes(x=vb,y=dist,fill=condit)) + 
#   stat_bar + facet_wrap(Fit_Method~Best_Model,ncol=2)
# 
# d |> group_by(condit,Fit_Method,Best_Model) %>% tally() |> mutate(n=n/6)
# 
# d |> group_by(condit,Fit_Method,Best_Model) |> filter(abs(Error_difference)>15) |> tally() |> mutate(n=n/6)
# 
# d |> group_by(condit,Fit_Method) |> mutate(m=mean(Error_difference), 
#                                               sd=sd(Error_difference), 
#                                               n=n()/6,se=sd/sqrt(n)) |>
#    group_by(condit,Fit_Method,Best_Model) |> 
#  # filter(abs(Error_difference)>(2.5*se)) |> 
#   ggplot(aes(x=vb,y=dist,fill=condit)) + 
#   stat_bar + facet_wrap(Fit_Method~Best_Model,ncol=2)
#

>>>>

ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
nbins <- 3
e1Sbjs <- ds |> group_by(id,condit) |> summarise(n=n())
fd <- readRDS(here("data/e1_08-21-23.rds"))
test <- testE1 <-  fd |> filter(expMode2 == "Test") 
testAvgE1 <- testE1 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vxAvg=mean(vx),distAvg=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

post_dat <- post_dat |> 
 left_join(testAvgE1 |> 
             select(id,condit,bandInt,bandType,vb,bandInt), 
           by=join_by(id,condit,x==bandInt))

post_dat_l <- post_dat_l |> 
 left_join(testAvgE1 |> 
             select(id,condit,bandInt,bandType,vb,bandInt), 
           by=join_by(id,condit,x==bandInt))

@@

agg_x_full_bt <-  post_dat  |> group_by(condit,Model,Fit_Method,x,bandType) |> 
 summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
    group_by(condit,Model,Fit_Method,x,bandType) |> 
    summarise(mean_error=mean(mean_error)) |> 
    round_tibble(1)

agg_x_full_bt |> 
  filter(!(Fit_Method=="Train")) |>
  mutate(Fit_Method=rename_fm(Fit_Method)) |>
  rename("Band"=x) |>
  flextable::tabulator(rows=c("Fit_Method","condit","Model","bandType"), columns=c("Band"),
                       `ME` = as_paragraph(mean_error)) |> as_flextable()

agg_x_full_bt |> 
  filter((Fit_Method=="Test_Train")) |>
  mutate(Fit_Method=(Fit_Method)) |>
  rename("Band"=x, "Condition"=condit) |>
  pander::pandoc.table(style="rmarkdown", split.table=Inf)

post_tabs$agg_pred_full_bt |> 
   pander::pandoc.table(style="rmarkdown", split.table=Inf)

post_tabs$agg_pred_full |> 
   pander::pandoc.table(style="rmarkdown", split.table=Inf)

@@

pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) 
pd <- post_dat |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt"))

@@

# extract id's from term column - Intercept is id 1, term=ModelEXAM doesn't have an id, so don't include
k <- b3_coef |> filter(term!="Intercept" & term!="ModelEXAM") |> mutate(id=as.factor(str_extract(term,"\\d+"))) |> left_join(testAvgE1 |> filter(bandInt==100) |> ungroup() |> select(-bandType,-vb,-bandInt),by="id") |> 
  mutate(exam_coef=exam_coef)

@@

k2 <- k |> filter(parType=="Model") |> mutate(id=reorder(id,Estimate), Estimate=Estimate+exam_coef) |> 
  select(id,condit,Estimate) |> left_join(testAvgE1,by=c("id","condit"))

@@

group_pred <- post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=val,y=vbLab,col=Resp)) + 
  stat_pointinterval(position=position_dodge(.5), alpha=.9) + 
  scale_color_manual(values=wes_palette("AsteroidCity2"))+
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
  labs(title="Posterior Predictions - Testing Stage",y="Velocity Band (lower bound)", x="X Velocity") +
theme(legend.title=element_blank(),axis.text.y = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

```{r}
#| fig-height: 12
#| fig-width: 11
 post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=condit,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~Resp, axes = "all",ncol=3,scale="free")

post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free")

p1 <- post_dat_l |> 
  filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

p2 <- post_dat_l |> 
  filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=Resp,y=val,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

@@

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=condit)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~vbLab, axes = "all",ncol=2,scale="free")

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=Resp,y=val,fill=condit)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~vbLab, axes = "all",ncol=2,scale="free")

@@

# d <- testAvgE1 |> left_join(full_comparison, by=c("id","condit")) |> filter(Fit_Method=="Test_Train")
# 
# 
# 
# d |> ggplot(aes(x=vb,y=vx,fill=condit)) + stat_bar + facet_wrap(Fit_Method~Best_Model2,ncol=2)
# 
# d |> 
#   group_by(condit,Fit_Method,Best_Model) |> 
#   mutate(nGrp2=n()) |>
#   filter(abs(Error_difference)>15) |> 
#   ggplot(aes(x=vb,y=dist,fill=condit)) + 
#   stat_bar + facet_wrap(Fit_Method~Best_Model,ncol=2)
# 
# d |> group_by(condit,Fit_Method,Best_Model) %>% tally() |> mutate(n=n/6)
# 
# d |> group_by(condit,Fit_Method,Best_Model) |> filter(abs(Error_difference)>15) |> tally() |> mutate(n=n/6)
# 
# d |> group_by(condit,Fit_Method) |> mutate(m=mean(Error_difference), 
#                                               sd=sd(Error_difference), 
#                                               n=n()/6,se=sd/sqrt(n)) |>
#    group_by(condit,Fit_Method,Best_Model) |> 
#  # filter(abs(Error_difference)>(2.5*se)) |> 
#   ggplot(aes(x=vb,y=dist,fill=condit)) + 
#   stat_bar + facet_wrap(Fit_Method~Best_Model,ncol=2)
#
